Baseline centering problem

### 2018-12-19 paper/tangotd.tex

>>>>

On-policy, working with $\gamma\to 1$ is quite easy: indeed $Z(s_1,s_2)$ is
a density with respect to $\mu(s_2)$ so that the asymptotics when
$\gamma\to 1$ is $Z(s_1,s_2)=\frac{1}{1-\gamma}+Z_0(s_1,s_2)$, and we can
directly learn $Z_0$ by inserting $\frac{1}{1-\gamma}+Z_0$ in the middle
Bellman equation. TODO check for simplifications.
